Proportional multi-state multiple-cohort life table model

### 2018-04-05 MSLT/MSLTdoc.Rmd
Comments on data for case studies

####Data for example (CHANGE TO ENGLISH DATA, MAY NOT BE AN EXAMPLE, BUT HAVE THE DATA FOR THE CASE STUDIES (NEED TO PREPARE: LONDON, SAO PABLO, DELHI, ACCRA, LOS ANGELES, EDINBURGH)). DATA AVAILABILITY FROM GBD AT WHAT LEVEL?

>>>>

####Data for example (CHANGE TO ENGLISH DATA, MAY NOT BE AN EXAMPLE, BUT HAVE THE DATA FOR THE CASE STUDIES (NEED TO PREPARE: LONDON, SAO PABLO, DELHI, ACCRA, LOS ANGELES, EDINBURGH)). DATA AVAILABILITY FROM ARE IN 5 YEARS UP TO 95+. gbd DATA IS NOT AVAILABLE AT THE CITY LEVEL, HOWEVER, SOME LEVEL OF DISSAGREAGATION IS AVAILABLE. ENGLAND: EAST MIDLANDS, EAST OF ENGLAND, GRETER LONDON, ETC. wE COULD USE GREATER LONDON. FOR EDINBURGH WE HAVE DATA FOR SCOTLAND.  FOR SAO PABLO, DATA IS FOR BRAZIL. MEXICO IS NOT LISTED, BUT GBD HAS DATA FOR DISTRITO FEDERAL. FOR DELHI THE DATA IS FOR INDIA. FOR ACCRA THE DATA IS FOR GHANA. FOR LOS ANGELES DATA IS FOR UNITED STATES, BUT WE CAN HAVE THIS FROM NEIL?
